Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-14 paper/reviewers-response.Rmd

> "I think the concepts presented in this manuscript are a useful addition to the literature on management of ecological networks.  I agree with the authors that it is important that the discussion surrounding what constitutes a 'keystone' species should go beyond centrality metrics. I found the results and concepts to be generally well presented, particularly graphically, and the authors present a thorough sensitivity analysis to various assumptions.

We are very thankful for the positive feedback but also for the issues highlighted. We have aimed to address them all.

> "The methods are mostly clear but there is no description of how the 'likelihood of being a superior node' is calculated."

<!-- DBS: Don't you think they're asking for this to appear in the main text and not the supps? -->
<!-- FDO: The 'probability/likelihood of being a superior node' is not mentioned in the main text, not even once. It only briefly gets mentioned in the Results and the Discussion and that is more in the conceptual way of what it means to be superior node. Not on how we devise this 'likelihood' when we have multiple non-reciprocal instances of a network. Plus in the paper, we don't really get much ecological insight from it. Because it's only mentioned in the supp. info I added this there and I think that'll be fine. We can always change it if they come back to it -->
*Accepted and changed*. Thanks for pointing this out. We have modified the sentence mentioning 'the likelihood of being a superior node' in the first paragraph of the section \@ref(S-reciprocal-links) to "...and whether it is a superior node..." to avoid confusion. Then we define the 'probability of being a superior node' at the end of the section: "It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network. 
We, therefore, denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community".

@@

> "*L1364*: 'dynamic persistence'"

*Accepted and changed*: Thank you. To avoid confusion we have removed the word 'dynamic' and now the sentence reads "...our results suggest that structural controllability is closely related to the persistence..." (\lr{M-R2-dynamic-persistence}). This preserves meaning without sacrificing precision.

> "*L1370*: 'dynamic stability'"

*Accepted and changed*: Contrastingly, in this case, the word dynamic distinguishes a particular facet of stability. We mean the ability of the system to return to an equilibrium state after a perturbation. We now include this definition on \lr{M-R2-dynamic-stability} to make the concept clearer.

@@

> "How were the model sets derived? Were all possible sub-models compared or was a step-wise approach used?"

*Accepted and changed*: We actually compared all possible candidate models. We have edited the manuscript on \lr{M-R2-all-candidates} to include this information.

> "Reciprocal links were included in the directed graph when dij = dji. Would it have any effect if there was a little wiggle room there, e.g., when the two are close but not equal?"

Rather than add yet another layer of complexity to our manuscript and given the rapid turnaround of the revised manuscript, we did not conduct this added sensitivity check. However, we note that only a very small fraction of interactions had a small asymmetry (see Figure R1). We, therefore, don't expect our results to change considerably even when we include reciprocal links when the asymmetry is small but not zero.
<!-- DBS: Why don't we say something to this effect in the main text to throw them a bit of a bone? -->
<!-- FDO: Humm. I cannot find a good place to put this in the main text without having to write a half/full paragraph about it... -->

### 2019-01-14 paper/supp-info.Rmd
Typos and commas in the response to reviewers

All of these non-reciprocal networks are as likely to be one that best represents the superior/matched relationships in the network. 
As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network. 
We therefore denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.

>>>>

All of these non-reciprocal networks are as likely to be one that best represents the superior/matched relationships in the network. 
As such, we average the three metrics ($n_D$, $\phi$, and $\sigma$) across all the networks without reciprocal links without weighting by the number of possible control configurations. 
It is important to note that a species that is found to be a superior node under a particular control configuration will be so in all possible control configurations for the particular non-reciprocal network. 
We, therefore, denote the average of $\sigma$ across all non-reciprocal versions as the probability of the species being a superior node in its community.
